Why Donors Donate: Disentangling Organizational and Structural Heuristics for International Philanthropy

### 2019-06-25 manuscript/manuscript.Rmd
Placeholders for Methods and Results sections
Outline model results

>>>>

# Methods

# Results

- First set of questions (hypotheses) can be answered using the results of the intercept-only model.
- Second set of questions (confirmatory) can be answered using the following upper-level models:
  - Public affairs: `Donation preferences ~ Public affairs knowledge + Public affairs activity`
  - Political ideology: `Donation preferences ~ Political ideology`
  - Social views: `Donation preferences ~ Public affairs trust + Social ideology + Religiosity`
  - Charity and voluntarism: `Donation preferences ~ Charity trust + Charity activity + Volunteer activity + Activism activity + Association membership`
  - Demographics: `Donation preferences ~ Gender + Marital status + Education + Income + Race + Age`
  - `Donation preferences ~ (Public affairs) + (Political ideology)`
  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views)`
  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism)`
  - `Donation preferences ~ (Public affairs) + (Political ideology) + (Social views) + (Charity and voluntarism) + (Demographics)`
- Third set of questions (exploratory) can be answered using a market simulator.
